### 2020-05-26 writeup/experiments.tex
update figure 2

\begin{figure}[!ht]
	\centering
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.95\textwidth]{figures/ratio_alignment_norm_lstm.pdf}
		\caption{LSTM (averaged)}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.95\textwidth]{figures/ratio_alignment_norm_mlp.pdf}
		\caption{MLP (averaged)}
	\end{subfigure}\hfill
		\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.95\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
		\caption{LSTM for one pair}
	\end{subfigure}
	\caption{The performance of aligning task covariances depends on data size.}
	\label{fig_covariate}
\end{figure}

>>>>

\begin{figure}[!ht]
	\centering
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
		\caption{LSTM (averaged)}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
		\caption{MLP (averaged)}
	\end{subfigure}\hfill
		\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
		\caption{LSTM for one pair}
	\end{subfigure}
	\caption{The performance of aligning task covariances depends on data size.}
	\label{fig_covariate}
\end{figure}
